Multimodal Corpora

### 2017-01-16 paper.tex
Add more subsections to the second corpus

%Acronyms
\newacronym{saga}{SaGA}{Bielefeld Speech and Gesture Alignment}
\newacronym{dfg}{DFG}{German Research Foundation}
\newacronym{lrec}{LREC}{Language Resources and Evaluation Conference}
\newacronym{vr}{VR}{Virtual Reality}
\newacronym{asl}{ASL}{American Sign Language}

@@

	\section{The CALLAS Expressivity Corpus}
		The yet to be released CALLAS Expressivity Corpus is part of the \gls{callas} project \cite{2010MultimodalCorpusForGestureExpressivity}. It was introduced in 2010 \cite{2010MultimodalCorpusForGestureExpressivity} and further described in \cite{Caridakis2013} three years later. All the information in this section is taken from those two papers if not stated otherwise, as this corpus was not released to the public yet, so there is no other information source besides a paper from one of the collaborators\cite{wagner:2011:1}. This corpus was a collaboratiove work between the National Technical University of Athens (G. Caridakis, A. Raouzaiou, K. Karpouzis), the Augsburg University (J. Wagner, F. Lingenfelser, E. Andre) and Humanware S.r.l. (Z. Curto). The available modalities are audio, video and hand gestures recorded separately in three different ways. 
		\subsection{Motivation}
			The main focus for this corpus was to capture cross-cultural differences in expressing emotoions with hand gestures. Obtaining the data which is needed to investigate the differences in cultures was done by collecting data in Greece, Germany and Italy as well. Another motivation was the recording of material which is as realistic as possible. This led the team to use persons without any background as actor, with the result that the data's variance is high, which is better to model the real world as the emotion expression of humans may vary greatly.

>>>>

%Acronyms
\newacronym{saga}{SaGA}{Bielefeld Speech and Gesture Alignment}
\newacronym{dfg}{DFG}{German Research Foundation}
\newacronym{lrec}{LREC}{Language Resources and Evaluation Conference}
\newacronym{vr}{VR}{Virtual Reality}
\newacronym{asl}{ASL}{American Sign Language}
\newacronym{ssi}{SSI}{Smart Sensor Integration}

@@

	\section{The CALLAS Expressivity Corpus}
		The yet to be released CALLAS Expressivity Corpus is part of the \gls{callas} project \cite{2010MultimodalCorpusForGestureExpressivity}. It was introduced in 2010 \cite{2010MultimodalCorpusForGestureExpressivity} and further described in \cite{Caridakis2013} three years later. All the information in this section is taken from those two papers if not stated otherwise, as this corpus was not released to the public yet, so there is no other information source besides a paper from one of the collaborators\cite{wagner:2011:1}. This corpus was a collaborative work between the National Technical University of Athens (G. Caridakis, A. Raouzaiou, K. Karpouzis), the Augsburg University (J. Wagner, F. Lingenfelser, E. Andre) and Humanware S.r.l. (Z. Curto). The available modalities are audio, video and hand gestures recorded separately in three different ways. 
		\subsection{Motivation}
			The main focus for this corpus was to capture cross-cultural differences in expressing emotions with hand gestures. Obtaining the data which is needed to investigate the differences in cultures was done by collecting data in Greece, Germany and Italy as well. Another motivation was the recording of material which is as realistic as possible. This led the team to use persons without any background as actor, with the result that the data's variance is high, which is better to model the real world as the emotion expression of humans may vary greatly.
		\subsection{Recording Scenario}
			The conducted experiment is split into three blocks which are then again split in three smaller parts. The difference between those bigger blocks is the emotion, which should be expressed by the proband. The method used to set the proband in a specific emotional mood was the Velten Mood Induction method \cite{VeltenJr1968473}. Using this method the user was free to modify the given sentence and was encouraged to make a gesture fitting the emotional mood. In the smaller sections three different gesture capturing methods were used.
		\subsubsection{Experiment Setup}
			Many devices were used to record the data which are then incorporated into the corpus. The sentence to read aloud is projected onto the wall in front of the proband. Behind the user is a neutral background. Two cameras are positioned before the proband to capture the face and one to capture the whole upper body. They have a resolution of 720x576px, 24bit color depth and 25 fps. Audio was recorded using a microphone above the head with a samplerate of 16 kHz as mono. Gestures were recorded using a computer vision approaches to detect the hands and the head, a Nintendo Wii remote for each hand or a data glove from Humanware. All datastreams were synchronized with a global clock by \gls{ssi} \cite{SmartSensorIntegration2010}.
		\subsection{Recorded Data}
			The corpus has 15 hours 14 minutes and 24 seconds of footage from all the three modalities. Audio is given by the sound which is recorded by the microphone. Video is available in two channels as two cameras were used for recording. One channel has shows the face and shoulder from the user. The other camera recorded the whole upper body including the hands, which is then used for gesture recognition. Gestures were captured by using three different methods. The first method was to use the video of the second camera which is then used to calculate the 2d position of the hand. The second method was to use the Wii remote to track the hands by capturing the data from the inbuilt accelerometer. The last approach to analyze the gestures executed by the probands is to use the data glove from Humanware which records the angles between the finger joints.
		\subsection{Application}
			c
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
